% This LaTeX document needs to be compiled with XeLaTeX.
\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{ucharclasses}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=magenta, urlcolor=cyan,}
\urlstyle{same}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}
\usepackage{stmaryrd}
\usepackage[fallback]{xeCJK}
\usepackage{polyglossia}
\usepackage{fontspec}
\setCJKmainfont{Noto Serif CJK TC}

\setmainlanguage{english}
\setotherlanguages{polish}
\newfontfamily\lgcfont{CMU Serif}
\setDefaultTransitions{\lgcfont}{}

\begin{document}
\section*{Shuang Song}
\section*{Independent Developer for Algorithms \& Contracts. PY/RS/CPP/SOL.}
\section*{Profile}
Experienced Job Types:

\begin{itemize}
  \item 6 years Machine Learning Engineer
  \item 3 years Smart Contract Engineer
  \item 3 years Rust EVM Engineer
\end{itemize}

Expected Job Types:

\begin{itemize}
  \item Machine Learning Engineer, Smart Contract Engineer, Smart Contract Auditor
  \item HongKong On-site \& Remote
  \item Europe Remote \& VISA supported On-site
\end{itemize}

\section*{Professional Experience}
09/2020 - 07/2023\\
Remote, Japan

08/2018 - 09/2020\\
Remote, Japan

02/2016 - 08/2018\\
Shanghai, China

\section*{Web3 Smart Contract Engineer}
SPARTICLE INC. JAPAN\\
Developed and deployed performant Solana smart contracts using Rust cooperating a 30 members all-remote team, achieving around 3500 TPS and handling 3000 concurrent users. Proficient in the Solana toolchain, including the Solana CLI, Anchor framework for streamlined development, and Solana Program Library (SPL) for token management and other common functionalities. Experienced in optimizing contract execution for minimal gas fees and secure onchain interactions.

\section*{Quantitative Financial Engineer}
INVEST INC. JAPAN\\
Developed quantitative trading models using Python and PyTorch with a small group of experts, achieving a Sharpe ratio of 3.3 and an annualized return of around 26\%. Implemented advanced time series analysis, machine learning algorithms (including deep neural networks), and backtesting frameworks. Generated daily CTA (Commodity Trading Advisor) reports, providing actionable insights for portfolio management and risk assessment.

\section*{Computer Vision Engineer}
SUNNATECH SHANGHAI CO, LTD.\\
Built, deployed, tested a Tensorflow based medical Images classification system with a 20 members team and applied it on the primitive screening of 7 diseases in 4 local clinic radiology departments, achieving an over-all F1 score of 0.78 of all recorded cases.

\section*{Projects}
01/2022 - 05/2022

01/2021 - 02/2021

01/2018 - 02/2018

08/2011-08/2014\\
Shanghai, China

08/2005 - 08/2010\\
Chengdu, China

MY RUST SIDE PROJECT\\
\href{https://github.com/ssghost/My_Resume/blob/main/My_Rust_Sideproj.md}{https://github.com/ssghost/My\_Resume/blob/main/My\_Rust\_Sideproj.md} 5 versatile pure Rust based applications written all by myself including Defi app, Quant trading indicator, Backend, Hardware driver, and Terminal interfaces.

\section*{MY BLOCKCHAIN TECHSTACK}
\href{https://github.com/ssghost/My_Resume/blob/main/My_BlockChain_TechStack.md}{https://github.com/ssghost/My\_Resume/blob/main/My\_BlockChain\_TechStack.md} 10 practical blockchain projects created all by myself, including: Basic Contracts, Distributions of ERC20 Token, ERC721 NFT, ERC 1202 DAO, MEV, Querying of NFT, zkSync Enhancements, and a complete Rust backend supported Defi App.

MY DEEPLEARNING TECHSTACK\\
\href{https://github.com/ssghost/My_Resume/blob/main/My_DeepLearning_TechStack.md}{https://github.com/ssghost/My\_Resume/blob/main/My\_DeepLearning\_TechStack.md} 10 practical deep-learning projects created all by myself, including: CNN, RNN, RL, NLP, GAN, Transformers, Computer Vision, Financial Decisions, Stable Diffusions.

\section*{Education}
\section*{Master of Medicine}
Shanghai Marine Medical University $\lceil$ Research Subject: Cell Plasticity and RNA Interferences Author and Co-author of 3 International SCI Papers during studying period.

\section*{Bachelor of Medicine}
Southwest Medical University ©兀 Research Subject:\\
Diagnostic Radiology

\section*{Certificates}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Certified Blockchain Solidity Developer & Certified Kubernetes Application Developer Ł & Coursera Deep Learning Specializations ㄷ \\
\hline
\multicolumn{3}{|l|}{Advanced} \\
\hline
 & Coursera Tensorflow in Practice & Chainlink Oracles Foundation \\
\hline
Coursera Machine Learning & Specializations ${ }^{\text {J }}$ & ■ \\
\hline
Specializations $\square$ &  & Master Class \\
\hline
\end{tabular}
\end{center}

\section*{Skills}
Python\\
Javascript\\
Rust\\
Julia\\
Translation\\
Graphic Design

C++\\
Typescript\\
Solidity\\
SQL\\
Statistics\\
Scientific Writing


\end{document}