\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}
\usepackage{stmaryrd}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=magenta, urlcolor=cyan,}
\urlstyle{same}

\title{Shuang Song }

\author{}
\date{}


\begin{document}
\maketitle
\section{Independent Developer for Algorithms \& Contracts. 
 $P Y / R S / C P P / S O L$.}
\href{mailto:shuangsong00@outlook.com}{shuangsong00@outlook.com}

Shanghai, China, Need VISA Support for Rebase

\href{https://github.com/ssghost}{https://github.com/ssghost}

\section{Profile}
Experienced Job Types:

\begin{itemize}
  \item 6 years Machine Learning Engineer
  
  \item 3 years Quantitative Engineer

  \item 2 years Smart Contract Engineer

\end{itemize}

Expected Job Types:

\begin{itemize}
  \item Machine-Learning engineer, Quantitative engineer, Smart contract engineer
\end{itemize}

\section{Professional Experience}
09/2021-07/2022

Remote, Japan

08/2018 - 09/2021

Remote, Japan

$02 / 2016-08 / 2018$

Shanghai, China

$08 / 2012-02 / 2014$

Shanghai, China Smart Contract Engineer

SPARTICLE INC. JAPAN

Deployed and managed a React based large-scaled instant message web service for business uses with a 30 members all-remote team, built and published a Solidity based NFT token system related with the IM service almost alone within 2 weeks.

\section{Quantitative Financial Engineer}
INVEST INC. JAPAN

Participated in an expert team of about 25 members to build and deploy some financial-oriented ML systems of quantitative strategy designing to help customers to acquire maximum profits in the stock market of Japan, managed to build a complete workflow of Deep Reinforcement Learning by myself.

\section{Computer Vision Engineer}
SUNNATECH SHANGHAI CO, LTD.

Built, deployed, tested a Tensorflow based medical Images classification system with a 20 members team and applied it on the primitive screening of 7 diseases in 4 local clinic radiology departments.

\section{Fellow Researcher}
CHINESE NATIONAL NATURE SCIENCE FOUNDATION PROJECT RNA INTERFERENCE THERAPY TEAM

This was my master's degree related research project. I learned all the foundations of data analytics and programming skills during the studying period. I completed and published $3 \mathrm{SCI}$ papers during this period. MY BLOCKCHAIN TECHSTACK

\href{https://gist.github.com/ssghost/b4e72af022b48312f039c23289386373}{https://gist.github.com/ssghost/b4e72af022b48312f039c23289386373}

10 practical blockchain projects created all by myself, including: Basic Contracts, Distributions of ERC20 Token, ERC721 NFT, ERC 1202 DAO, MEV, Querying of NFT, zkSync Enhancements.

$01 / 2018-02 / 2018$

\section{MY DEEPLEARNING TECHSTACK}
\href{https://gist.github.com/ssghost/b729229d3e061b07d2983005b2427153}{https://gist.github.com/ssghost/b729229d3e061b07d2983005b2427153}

10 practical deep-learning projects created all by myself, including: CNN, RNN, RL, NLP, GAN, Transformers, Computer Vision, Financial Decisions, Stable Diffusions.

\section{Education}
$08 / 2011-08 / 2014$

Shanghai, China

$08 / 2005-08 / 2010$

Chengdu, China

\section{Master of Medicine}
Shanghai Marine Medical University $\square$

Research Subject:

Cell Plasticity and RNA Interferences

Author and Co-author of 3 International SCI Papers during studying period.

\section{Bachelor of Medicine}
Southwest Medical University $]$

Research Subject:

Diagnostic Radiology

\section{Certificates}
\section{Certified Blockchain Solidity}
 Developer $\square$Advanced

Coursera Deep Learning Specializations $]$ Certified React.js Developer $\square$ Advanced

Coursera Machine Learning

Specializations $\square$ Certified Kubernetes Application Developer $\square$

Coursera Tensorflow in Practice Specializations $[\bar{C}$

\section{Skills}
Python

Javascript

Rust

Julia $\mathrm{C}++$

Typescript

Solidity

SQL

\section{Languages}
English

IELTS 6.5 CET6 553 Chinese

Mother language Japanese

JPLT N2


\end{document}