\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=magenta, urlcolor=cyan,}
\urlstyle{same}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}
\usepackage{stmaryrd}

\title{Shuang Song }

\author{}
\date{}


\begin{document}
\maketitle
Independent Developer for Algorithms \& Contracts. PY/RS/CPP/SOL.

\section*{Profile}
Experienced Job Types:

\begin{itemize}
  \item 6 years Machine Learning Engineer
  \item 3 years Smart Contract Engineer
  \item 3 years Rust EVM Engineer
\end{itemize}

Expected Job Types:

\begin{itemize}
  \item Machine Learning Engineer, Smart Contract Engineer, Smart Contract Auditor
  \item HongKong On-site \& Remote
  \item Europe Remote \& VISA supported On-site
\end{itemize}

\section*{Professional Experience}
09/2020 - 07/2023\\
Remote, Japan

08/2018 - 09/2020\\
Remote, Japan

02/2016 - 08/2018\\
Shanghai, China

08/2012 - 02/2014\\
Shanghai, China

\section*{Web3 Smart Contract Engineer}
SPARTICLE INC. JAPAN\\
Deployed and managed a React based large-scaled instant message web service for business uses and designed its fast responding backends and EVM architectures with Rust cooperating a 30 members all-remote team, built and published a Solidity based NFT token system related with the IM service almost alone within 2 weeks.

\section*{Quantitative Financial Engineer}
INVEST INC. JAPAN\\
Participated in an expert team of about 25 members to build and deploy some financial-oriented ML systems of quantitative strategy designing to help customers to acquire maximum profits in the stock market of Japan, managed to build a complete workflow of Deep Reinforcement Learning by myself.

\section*{Computer Vision Engineer}
SUNNATECH SHANGHAI CO, LTD.\\
Built, deployed, tested a Tensorflow based medical Images classification system with a 20 members team and applied it on the primitive screening of 7 diseases in 4 local clinic radiology departments.

\section*{Fellow Researcher}
CHINESE NATIONAL NATURE SCIENCE FOUNDATION PROJECT RNA INTERFERENCE THERAPY TEAM\\
This was my master's degree related research project. I learned all the foundations of data analytics and programming skills during the studying period. I completed and published 3 SCI papers during this period.

\section*{Projects}
01/2022 - 05/2022

01/2021 - 02/2021

01/2018 - 02/2018\\
08/2011 - 08/2014\\
Shanghai, China

08/2005 - 08/2010\\
Chengdu, China

\section*{MY RUST SIDE PROJECT}
\href{https://github.com/ssghost/My_Resume/blob/main/My_Rust_Sideproj.md}{https://github.com/ssghost/My\_Resume/blob/main/My\_Rust\_Sideproj.md} 5 versatile pure Rust based applications written all by myself including Defi app, Quant trading indicator, Backend, Hardware driver, and Terminal interfaces.

\section*{MY BLOCKCHAIN TECHSTACK}
\href{https://github.com/ssghost/My_Resume/blob/main/My_BlockChain_TechStack.md}{https://github.com/ssghost/My\_Resume/blob/main/My\_BlockChain\_TechStack.md} 10 practical blockchain projects created all by myself, including: Basic Contracts, Distributions of ERC20 Token, ERC721 NFT, ERC 1202 DAO, MEV, Querying of NFT, zkSync Enhancements, and a complete Rust backend supported Defi App.

\section*{MY DEEPLEARNING TECHSTACK}
\href{https://github.com/ssghost/My_Resume/blob/main/My_DeepLearning_TechStack.md}{https://github.com/ssghost/My\_Resume/blob/main/My\_DeepLearning\_TechStack.md} 10 practical deep-learning projects created all by myself, including: CNN, RNN, RL, NLP, GAN, Transformers, Computer Vision, Financial Decisions, Stable Diffusions.

\section*{Education}
\section*{Master of Medicine}
Shanghai Marine Medical University ${ }^{\square}$ Research Subject:\\
Cell Plasticity and RNA Interferences\\
Author and Co-author of 3 International SCI Papers during studying period.

\section*{Bachelor of Medicine}
Southwest Medical University ■ Research Subject:\\
Diagnostic Radiology

\section*{Certificates}
Certified Blockchain Solidity Developer ㄷ\\
Advanced

\section*{Coursera Machine Learning}
Specializations $[$

Certified Kubernetes Application Developer $\longleftarrow$

Coursera Tensorflow in Practice Specializations

\section*{Coursera Deep Learning Specializations}
Chainlink Oracles Foundation\\
■\\
Master Class

\section*{Skills}
Python\\
Javascript\\
Rust\\
Julia\\
Translation\\
Graphic Design

C++\\
Typescript\\
Solidity\\
SQL\\
Statistics\\
Scientific Writing


\end{document}